The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents

### 2023-02-27 figures/fig-heatmap_coverage.tex
Anastasia edit

\begin{figure*}[]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
  \label{fig:heatmap_coverage}
\end{figure*}

>>>>

\begin{figure*}[]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-heatmap_coverage.pdf}
  \caption{Number of past work that identified relationships between conversation architecture and the perception of agents (on the left) and number of past work that explored possible connections (on the right).}
  \Description{This figure shows a side-by-side comparison between the 183 identified relationships within the 265 explored connections in literature for conversation architecture elements and perceptions of agents. The visuals are shown as two heatmaps, with darker shades depicting a higher number of relationships. The numbers within each cell at the interaction of a specific conversation architecture element and perception aspect outlines the number of relationships found in the reviewed corpus.}
  \label{fig:heatmap_coverage}
\end{figure*}

### 2023-02-27 paper.tex
Anastasia edit

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

\ccsdesc{TBD}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversational architecture, anthropomorphized perceptions}

>>>>

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003120.10003121.10003126</concept_id>
       <concept_desc>Human-centered computing~HCI theory, concepts and models</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003120.10003121.10003122</concept_id>
       <concept_desc>Human-centered computing~HCI design and evaluation methods</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10003120.10003121.10003124.10010870</concept_id>
       <concept_desc>Human-centered computing~Natural language interfaces</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~HCI theory, concepts and models}
\ccsdesc[500]{Human-centered computing~HCI design and evaluation methods}
\ccsdesc[500]{Human-centered computing~Natural language interfaces}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{conversational agents, user perception, conversation architecture, anthropomorphized perceptions}

### 2023-02-27 sections/1-introduction.tex
Anastasia edit

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions~\cite{knijnenburg2016inferring, seeger2021chatbots}. According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.

While various studies investigated how different conversation architecture elements affect agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature. For conversation architecture elements, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances~\cite{diederich2019emulating, yang2017perceived}. Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}. However, there is a lack of research to synthesize these findings into an overall framework. One of the possible issues is the lack of clear and consistent definitions of the aspects of users' perceptions of agent and conversation architectural elements.

Currently, there is no systematic understanding on the elements of conversation architecture that are relevant to the perceptions of agents. Some papers have started to examine the speech specifics explored in literature, such as \citet{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics. There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA. Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues. However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.

Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations. Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs. These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g. empathy, humanness) alongside other assessments (e.g. physiological data) \cite{clark2019state, finch2020towards}. Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}. However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.

These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents. First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}. While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}

To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (\autoref{fig:heatmap_identified}). We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}). %Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework. Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents. 
This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users. 
%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents. With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.

In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus. Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture. Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.

>>>>

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents communicate in natural language, \textit{conversation architecture}---what and how a CA says---affects users' perceptions of agents and, in turn, the effectiveness of their interactions with users \cite{knijnenburg2016inferring, seeger2021chatbots}, i.e. supporting users in achieving users' goals. For instance, previous research suggests that there is a relationship between CAs' conversation architecture and how users perceive these agents %.
%While various studies investigated how some elements of conversation architecture affect users' perceptions of agents~
(e.g.,~\cite{clark2019state, feine2019taxonomy, finch2020towards}).  However, there is currently a lack of systematic understanding of these relationships, i.e. what elements of conversation architecture are impactful for users' perceptions and how. Specifically, while various studies investigated how some elements of conversation architecture affect some aspects of users' perceptions or discussed the speech specifics of agents as part of a broader analysis of the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for 
conversation architecture elements that are relevant to user perceptions. Yet, this systematic understanding is essential for guiding the design of conversation architecture, which would allow us to both predict and develop users' appropriate perceptions of agents.

%there is a lack of systematic understanding of these relationships.
%paucity of knowledge on the overall coverage and effects of these relationships explored in literature. 
%One reason for this disparity is, arguably, the lack of clear and consistent definitions of both the aspects of users' perceptions of agent and conversation architectural elements. Although some authors discuss the speech specifics of agents as part of a broader analysis on the state of research \cite{clark2019state,feine2019taxonomy}, there is no comprehensive analysis of %research specifically for 
%conversation architecture elements that are relevant to user perceptions. Similarly for user perceptions, while there is some research exploring the perceptions of agents as part of understanding the user experiences \cite{clark2019state, finch2020towards} or social cues \cite{feine2019taxonomy} of CAs, there is no exhaustive research specifically for perceptions of agents that are affected by conversation architecture elements.

%These research gaps related to the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents 
To address this gap, in this paper, we
%we aim to understand how to design conversation architecture in order to orchestrate perceptions of conversational agents.
%First, we 
explore the following research questions: \textbf{(RQ1) what aspects of users' perceptions of agents have been explored in relation to the effects of conversation architecture elements}, \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?}, and \textbf{(RQ3) what is known of the specifics of these relationships between conversation architecture elements and the perceptions of CAs?}
%While there are various elements of conversation architecture used in a CA's utterances, we don't have a systematic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to users' perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}
To answer these questions, we performed a comprehensive review of the existing literature published from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on the final dataset of 57 relevant papers (\autoref{fig:heatmap_identified}). Based on this review, we grouped the perceptions of agents that were shown to be affected by conversation architecture into four categories and eleven aspects (\autoref{tbl:perceptions}) and grouped the speech variations related to perceptions of agents into four categories and eleven elements (\autoref{tbl:conversation_architecture}). 
We found that perceptions of interaction with CAs (usability, engagement, satisfaction) have been most explored in relation to speech variations, while the perceptions of CAs' ability (intelligence, competence, credibility) have been explored the least.
%the least number of explored and identified relationships. 
Our results also show that the conversation architecture elements of response delay and agent-initiated dialog-related perceptions of CAs are under-explored in literature. 
Thus, this work contributes to the CUI community by presenting a framework that synthesizes the findings on the effect of conversation architecture on perceptions of conversational agents and identifies and clusters perception aspects and conversation architecture elements. %, providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users.

In the remainder of the paper, we first outline related background work, then describe the literature review process and the framework synthesis method, %, the characteristics of the papers in our reviewed corpus. Following that, we 
followed by a detailed description of the taxonomies of the aspects of the perception of agents and conversation architecture elements, as well as the synthesized framework for their relationships. We conclude by discussing the implications of this work, including 
the associated research challenges and opportunities, as well as ethical considerations for designing the conversational architecture to affect users' perceptions of conversational agents.

### 2023-02-27 sections/2-related_work.tex
Anastasia edit

\section{Related Work}

Communication with conversational agents is similar to communicating with humans as they both use natural languages for the interaction. While it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications. Currently people consider CAs as a user-controlled tool rather than a social companion, with focuses on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}. When conversing with conversational agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}. Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes, doyle2019mapping}\cmt{[1],[2]}. There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping, kim2022understanding}\cmt{[2],[3]}. Given human-agent communications are different from human-human communications, it is important to look specifically at the design of user experiences for conversational agents.

There have been numerous studies on the user experiences for conversational agents, and some attempts to synthesize findings across literature. Several papers have mapped out the current state of research for conversational agents for specific agent types (e.g. text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}. Other papers looked at specific dimensions of user experiences or domains of usage, such as Van Pinxteren et al. \cite{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and Kocaballi et al. \cite{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare. There are also publications aimed to unify concepts used in the research for CA user experiences, for instance Feine et al. \cite{feine2019taxonomy} creating a taxonomy of social cues, and Finch et al. \cite{finch2020towards} analyzing evaluation protocols for dialogue systems. To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.

@@

%Other papers categorized CA assessments into themes. For example, Rapp et al. \cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.  Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence. However, existing studies use different terminologies and categories across aspects of perception. As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al. \cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols

%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}. For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.  Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}. Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}. Anthropomorphism has been shown to ease user interactions, e.g. making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}. These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc. \cite{kuzminykh2020genie}.

>>>>

\section{Related Work}
%Communication with conversational agents 
Similar to human-human communication, human communication with conversational agents relies on natural languages for interaction. However, while it is tempting to leverage components from human-human conversation in designing interactions with conversational agents, studies have demonstrated that there are differences between human-human communications and human-agent communications \cite{clark2019makes, hill2015real}. Currently, CAs are considered as a user-controlled tool rather than a social companion, with a focus on the utilitarian aspects of the conversation \cite{clark2019makes}\cmt{[1]}. When conversing with agents, users tend to use shorter messages with limited vocabulary, adapting to the style of the agent \cite{hill2015real}. Also, some studies found that small talk and humour are considered unnecessary or even inauthentic in conversations with CAs, while these elements are important in scaffolding communications with human partners \cite{clark2019makes, doyle2019mapping}\cmt{[1],[2]}. There are also machine-like traits that users preferred in a CA, such as the ability to interact through multimodal media, and a machine's perceived ability to be objective and non-judgemental \cite{doyle2019mapping, kim2022understanding}\cmt{[2],[3]}. Given human-agent communications are different from human-human communications, it is important to look specifically at the design of user experiences for conversational agents.

There are a number of studies investigating factors affecting user experiences for conversational agents, which includes exploring the relationship between conversation architecture elements and agents' perceptions. For instance, the use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive responses based on user's utterances \cite{diederich2019emulating, yang2017perceived}. Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}. However, there is a paucity of research to synthesize these findings on user experiences with agents across literature.

In recent years, several papers have synthesized the current state of research for conversational agents for specific agent types (e.g. text-based, voice-based, polyadic) highlighting major trends, topics, methods and evaluating metrics \cite{clark2019state, rapp2021human, zheng2022ux}\cmt{[33][5]}. Other papers looked at specific dimensions of user experiences or domains of usage, such as \citet{van2020human} examining the effects of agents' human-like communicative behaviours on their relationships with users, and \citet{kocaballi2022design} exploring the challenges and opportunities of CAs in healthcare. There are also publications aimed to unify concepts used in the research for CA user experiences, for instance \citet{feine2019taxonomy} creating a taxonomy of social cues, and \citet{finch2020towards} analyzing evaluation protocols for dialogue systems. To the best of our knowledge, there is currently no synthesis on the speech specifics of CAs, the perceptions of agents, or the relationship between them.

@@

### 2023-02-27 sections/3-method.tex
Anastasia edit

This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.

\subsection{Data Collection}

Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

@@

The initial query retrieved 2901 unique publications. We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers. The fully body of these papers are then reviewed, selecting 49 papers that met the criteria. A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection. In total, we identified 57 relevant articles for analysis (see \autoref{fig:prisma}).

@@

The papers reviewed (n=57) were published between May 2011 and November 2022. More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}). The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals. Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4). 
%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).

@@

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. We used inductive thematic analysis to group these assessments into codes based on their meanings. For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]}. This step resulted in 83 unique codes. These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions. For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).

>>>>

%This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.

\subsection{Data Collection}
To perform a literature analysis of past findings on the relationship between the specifics of conversation architecture and perceptions of CAs, we identified, reviewed, and selected relevant literature using PRISMA guidelines \cite{prisma}. %, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. 
Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

@@

The initial query retrieved 2901 unique publications. We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers. The fully body of these papers were then reviewed, selecting 49 papers that met the criteria. A search for additional literature based on citation tracing was also performed to supplement the corpus, adding 8 more papers to the selection. In total, we identified 57 relevant articles for analysis (see \autoref{fig:prisma}).

@@

The papers reviewed (n=57) were published between May 2011 and November 2022. The majority of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}). The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals. Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4). 
%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).

@@

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. We used inductive thematic analysis to group these assessments into codes based on their meanings. For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]}. This step resulted in 83 unique codes. These codes are then organized based on similarity of the meanings, resulting in 11 aspects of perceptions. For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).

### 2023-02-27 sections/4-findings.tex
Anastasia edit

As shown in \autoref{tbl:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception. The details of each category and aspect are discussed below.

@@

\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents. This category includes perception aspects of conversation tone, social presence and intimacy. \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness. Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm. \textit{Social presence} captures the sense of connectedness and psychological distance users have with an agent. Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them. The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent. Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}. These questionnaires include questions like ``\textit{I think the agent could be a friend of mine}'', or ``\textit{I feel we could establish a personal relationship with each other}''.

@@

Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus. The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness. There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent. This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction. This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al. in their discussions \cite{linnemann2018can}\cmt{[15]}. The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions. 
%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.

@@

As shown in \autoref{tbl:conversation_architecture}, there are four categories defined for conversation architecture across 12 different elements. The details of each category and element are discussed below.

>>>>

As shown in \autoref{tbl:perceptions}, we defined four categories for the perceptions of conversational agents covering 11 different aspects of perception. The details of each category and aspect are discussed below.

@@

\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents. This category includes perception aspects of conversation tone, social presence and intimacy. \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness. Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm. \textit{Social presence} captures the sense of connectedness and psychological distance users have with an agent. Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or has similar attitudes to them. The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent. Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}. These questionnaires include questions like ``\textit{I think the agent could be a friend of mine}'', or ``\textit{I feel we could establish a personal relationship with each other}''.

@@

Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus. The perception of interaction with agent is the most commonly explored category, followed by the perception of agent's humanness. There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent. This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction. This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al. in their discussions \cite{linnemann2018can}\cmt{[15]}. The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions.

@@

As shown in \autoref{tbl:conversation_architecture}, we defined four categories for conversation architecture across 12 different elements. The details of each category and element are discussed below.
